\documentclass{article}

\usepackage{thumbpdf}
\usepackage[pdftex, hidelinks]{hyperref}
\usepackage{arlres}
\usepackage{multicol}
\usepackage{fontawesome}
\linespread{1.05}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\RequirePackage{soul,colortbl,color}
\usepackage{enumerate}
\usepackage{fancyhdr}
\pagestyle{fancy}

\parskip=1ex
\parindent=0pt

\usepackage[top=0.7in, bottom=0.7in, left=0.85in,
  right=0.85in]{geometry}

\setmainfont[Ligatures=TeX,Scale=1.05]{Linux Libertine O}


\begin{document}

\begin{center}
  {\Large \bf Alexander R. Lange}\\[0.5em]
    {\small 710 Laurel Ave, San Mateo, CA 94401 $\;\bullet\;$
      (585)$\:$469-6313}\\
    {\small
      {\tt\href{mailto:alexlange257@gmail.com}{alexlange257@gmail.com}}
      $\;\bullet\;$}
    \faLinkedinSquare
    {\small
      $\;${\tt\href{https://www.linkedin.com/in/alexrlange}{alexrlange}}
%      $\;\bullet\;$}
%    \faGithub
%    {\small $\;${\tt\href{https://github.com/arlange}{arlange}}
  }
\end{center}

\vspace*{-1em}

\ressec{Summary}
\vspace*{0.25em}
\begin{tightcenter}
Backend software engineer with a strong mathematics background and experience researching,
developing, and maintaining web APIs and computer vision/machine learning pipelines.
\end{tightcenter}

\vspace*{-0.25em}

\ressec{Experience}

\vspace*{-0.25em}

\resentry{{\bf Neurotrack}}{Redwood City, CA}
\resentry{{\it Software Engineer}}{June 2015 -- present}
\begin{reslist}
  \item Researched. developed, and brought to production a webcam eye-gaze estimation tool for measuring subconscious novelty preference.
  Included initial prototyping and analysis, cross validation, feature selection, model architecture, and internal tools to manually evaluate and accept/reject results.
    \textcolor{darkgray}{\textbf{[}\textsf{Python}, \textsf{Django}, \textsf{OpenCV}, \textsf{scikit-learn}, \textsf{dlib}\textbf{]}}
  \item Developed, brought to production, and maintained backend RESTful APIs and full-stack web applications for projects including a
    consumer health app and a platform for deploying research studies involving company's tests.\\
    \textcolor{darkgray}
    {\textbf{[}\textsf{Python}, \textsf{Django}, \textsf{Postgres}, \textsf{Celery}, \textsf{Redis}, \textsf{Docker},
    \textsf{AWS}, some \textsf{Javascript}, \textsf{React}\textbf{]}}
  \item Researched and developed fixation/saccade detection algorithm, classifier to judge noisiness,
     and other analysis tools for
     raw eye-tracking data. \textcolor{darkgray}{\textbf{[}\textsf{Python}, \textsf{scikit-learn}, \textsf{numpy}\textbf{]}}
  \item Engineering liaison between company and clinical studies. Developed, deployed, and supported software on remote laptops.
     Improved company's remote data syncing process.
\end{reslist}

\vspace*{0.25em}

\resentry{{\bf Google}}{Mountain View, CA}
\resentry{{\it Software Engineer in Test Intern}}{September 2014 --
  December 2014}
As part of the \textsf{Ads Backend Engineering Productivity} team, I worked on the following
projects \textcolor{darkgray}{\textbf{[}all coding in \textsf{Python}\textbf{]}}:
\begin{reslist}
  \item Designed and developed a release automation workflow for the distributed data
    warehousing system of ads stats.
  \item Developed tools for the first stages of improving the code submission process
    of a particular team. Automated the generation of new golden files and diff reporting against
    older golden files.
\end{reslist}

\vspace*{0.25em}

\resentry{{\bf University of Waterloo}}{Waterloo, ON}
\resentry{{\it Research Assistant, Prof. Chaitanya Swamy}}{September 2013 -- May 2015}
Assisted in the design of approximation algorithms
for stochastic optimization problems.

%\resentry{{\it Teaching Assistant}}{September 2013 -- present}
%Ran tutorials, managed undergraduate markers, and marked assignments
%for MATH 135: Algebra for Honours Math, CO372: Portfolio Optimzation, and ECE 103: Discrete
%Math for Engineers.

\vspace*{0.25em}

\resentry{{\bf \rit}}{Rochester, NY}
\resentry{{\it Research Assistant, Prof. Stanis{\l}aw Radziszowski}}{January 2012 -- August 2013}
Designed and developed a robust library to generate, enumerate,
manipulate, and test graphs for a variety of Ramsey properties.
Deployed on the \emph{Open Science Grid}, using \textasciitilde 200,000 CPU hours.
Resulted in two publications. \textcolor{darkgray}{\textbf{[}\textsf{C++}\textbf{]}}

\vspace*{0.25em}

\resentry{{\bf Bell and Howell / BCC Software}}{Rochester, NY}
\resentry{\textit{Software Engineer Intern}}{June 2013 -- September 2013}
\resentry{\textit{Software Test Specialist/Quality Assurance
    Intern}}{June 2010 -- November 2011}

\vspace*{0.25em}

\ressec{Education}

\vspace*{-0.25em}

\resentry{\bf University of Waterloo}{Waterloo, ON}
\resentry{Master of Mathematics in Combinatorics and Optimization
  $\:$\textcolor{darkgray}{(concentration in Discrete Optimization)}
}{May 2015}
\begin{reslist}
  \item Thesis: \emph{Approximation Algorithms for Graph Protection Problems}
\end{reslist}

\vspace*{0.25em}

\resentry{\bf \rit}{Rochester, NY}
\resentry{Master of Science in Computer Science
  $\:$\textcolor{darkgray}{(concentration in Theory)}}{August 2013}
\begin{reslist}
  \item Thesis: \emph{Solving Hard Graph Problems with Combinatorial
    Computing and Optimization}
  \item Computer Science Outstanding Graduate Student Award, 2012--2013
  \item Placed 3rd out of 12 in the {\bf ACM-ICPC} Northeast North America Regional Finals, Fall 2012
\end{reslist}

\vspace*{0.25em}

\resentry{Bachelor of Science in {Computational Mathematics}}{May 2011}

\vspace*{0.25em}

\textbf{Languages/Tools Used}:
  \textcolor{darkgray}{
    Java, C++, Python, \LaTeX, {\sc Matlab}, SQL, C\#, .NET, Visual Studio, MIPS Assembly
  }


% \ressec{Skills}

% \begin{reslist}
% \item Proficient in Python, \LaTeX, {\sc Matlab}
% \item Academic experience with Java, C++, C\#, SQL, .NET
% \end{reslist}



% \vspace*{-0.5em}

% \ressec{Academic Awards and Achievements}
% \begin{reslist}
%   \item RIT Computer Science Outstanding Graduate Student Award, 2012--2013
%   \item Placed 3rd out of 12 in the {\bf ACM-ICPC} Northeast North America
% Regional Finals, Fall 2012
%   \item Golisano College of Computer and Information Sciences Research
%     Seed Funding, 2012 and 2013
%   %\item RIT Computer Science Graduate Delegate, nominated, Fall 2012
%   \item RIT Presidential Scholarship, 2007--2011; RIT Honors Program,
%     2007--2010%; RIT Dean’s List, 2007--2011
% \item {Publications}:\\[-1.75em]
% \begin{enumerate}{\footnotesize \renewcommand{\theenumi}{[\arabic{enumi}]}
%   \renewcommand{\labelenumi}{\theenumi}
%   {\partopsep=0pt \topsep=0pt \leftmargin=0em \parskip=0pt}
%   \setlength{\labelsep}{2pt}
%   \setlength{\itemsep}{-3pt}
%   \item A. Lange, S. Radziszowski, and X. Xu. Use of MAX-CUT for Ramsey
%     Arrowing of Triangles. \emph{Journal of Combinatorial Mathematics
%       and Combinatorial Computing}. \textbf{88} (2014) 61--71.
%   \item A. Lange, I. Livinsky, and S. Radziszowski. Computation of the
%       Ramsey Numbers $R(C_4,K_9)$ and $R(C_4,K_{10})$. \emph{accepted}.}
% \end{enumerate}
% \end{reslist}

%% \item {\bf Conference Presentations}: {\footnotesize 25th Cumberland Conf. on
%%   Combinatorics, Graph Theory, \& Computing, Johnson City, TN, May
%%   2012.  MIdwestern GrapH TheorY (MIGHTY) LIII Conference, Ames, IA,
%%   September 2012.  44th SE International Conf. on Combinatorics, Graph
%%   Theory, \& Computing, Boca Raton, FL, March 2013.}


\end{document}
